\clearemptydoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgments}	


%\chapter*{Acknowledgements}

\vspace*{2cm}

\begin{center}
{\Large \bf Acknowledgments}
\end{center}

\vspace{1cm}

First and foremost, I would like to express my very profound gratitude to Univ.-Prof. Dr. Hans-Joachim Bungartz and Univ.-Prof. Dr. Thomas Huckle for the opportunity to do my master thesis under their supervision and their support along the way any time I needed it.\\
My deepest sense of appreciation and thankfulness is towards my exemplary advisor Christoph Kowitz for his unconditional patience and support during the process of my master thesis. Without his patience I would not have been able to accomplish my task. His vision and knowledge on the subject and consequently, his continuous feedback have made my assignment much more comprehensible and straightforward. I would also like to thank my assistant advisor Alfredo Parra Hinojosa for his extra effort to steer me in the right direction and help me gain the confidence and encourage me to work harder later in the process.\\
I would like to acknowledge the great and endless opportunities I have been given to during my studies, from the admission to the program till the exceptional understanding of the CSE Examination Board to give me additional time to finish my thesis. I would also like to thank all the individuals involved in this regard. I feel obliged to say I am gratefully indebted to all.\\
Finally, I must articulate my very profound gratitude to my parents for nurturing me with immeasurable support throughout my life and to my friends for their heartfelt contribution along the process of writing this thesis. This accomplishment could not have been successfully achieved with you.